### 2022-05-06 paper/ase22/experiment.tex
exp restuls

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool.
%% \TODO{introduce details about each model}

@@

\begin{eqnarray}
  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
\end{eqnarray}

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
relevancy score between sentence and its associated \lc. Higer average
score means that higher human-level agreement of the use of sentence
for its \lc, resulting in higher suitability of the use of the
testcases for evaluating model on the \lc. Given the metrics, we
answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
and equation~\ref{metric:lcrel} respectively, thereby, show its
ability of \tool to understand human intelligence.

>>>>

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three leaerning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
searching seeds and expanding the seeds in \tool. The \Sstt is a
corpus of movie review, and it consists of 11,855 single sentences
with its sentiment score. As original dataset suggests, we split the
score range into [0, 0.4], (0.4, 0.6] and (0.6, 0.8] for assigning
    negative, neutral and positive labels respectively.
%% \TODO{introduce details about each model}

@@

\begin{eqnarray}
  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#Data\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
\end{eqnarray}

The equation~\ref{metric:srel} represent the number of test cases that
their labels assigned from are different between \tool and
human. Higher number of this metric indicates worse correlation of
test oracle that \tool generated with human. In addition, the
equation~\ref{metric:lcrel} represents the average score of the
normalized relevancy score between sentence and its associated
\lc. Higer average score means that higher human-level agreement of
the use of sentence for its \lc, resulting in higher suitability of
the use of the testcases for evaluating model on the \lc. Given the
metrics, we answer RQ1 and RQ2 by the metrics from the
equation~\ref{metric:srel} and equation~\ref{metric:lcrel}
respectively, thereby, show its ability of \tool to understand human
intelligence.

### 2022-05-06 paper/ase22/result.tex
table add
table
exp restuls

\section{Result}
\label{sec:result}

\subsection{RQ1: Can \tool generate consistent test sentence and
  its oracle?}

\InputWithSpace{tables/manual-study-table}

>>>>

\section{Experimental Results}
\label{sec:result}

This section presents experiment results and answer the RQs by
studying the results quantatively and qualitatively.

\InputWithSpace{tables/manual-study-table}
\InputWithSpace{tables/test-results-table}

\subsection{RQ1: \tool Sentiment Label Consistency}
Table~\ref{table:ManualStudy} shows the statistics of scores collected
from the manual study of \tool. First column represents type of test
case. The number of test cases used for the study is represented in
second column. Label consistency score and \lc relevancy score defined
at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
remaining columns. First, it is shown that high label consistency
score over 0.8. It means that \tool generates test oracles consistent
to human understanding. It is also observed that there is no
difference of the scores between seed and expanded sentences. The
observation implies that the expansion method in \tool preserves
sentiment of expanded sentences as its seed, and provides its
reliability. These observations answer RQ1 and conclude that \tool
generates test case with high consistency between test sentence and
its oracle.

\subsection{RQ2: Correctness of Linguistic Capability Categorization}
The result in table~\ref{table:ManualStudy} also shows that \tool
achieves high order of agreement with human assessment on \lc
relevancy. In parallel, it is observed that the expanded sentences
generated from \tool also have same level of \lc
relevancy. Accordingly, we answer the RQ2 by concluding that
\tool generates \lc relevant test cases with the agreement with human.

\subsection{RQ3: Test Suite Diversity}
\input{CM/coverage}

\subsection{RQ4: Use \tool for Debugging}

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
exp restuls

\DefMacro{test-results-bl-model0-lc0-num-fail}{3741}

@@

\DefMacro{test-results-bl-model0-lc1-num-fail}{799}

@@

\DefMacro{test-results-bl-model0-lc2-num-fail}{2427}

@@

\DefMacro{test-results-bl-model0-lc3-num-fail}{860}

@@

\DefMacro{test-results-bl-model0-lc4-num-fail}{1871}

@@

\DefMacro{test-results-bl-model0-lc5-num-fail}{1680}

@@

\DefMacro{test-results-bl-model0-lc6-num-fail}{1330}

@@

\DefMacro{test-results-bl-model0-lc7-num-fail}{26}

@@

\DefMacro{test-results-bl-model0-lc8-num-fail}{4056}

@@

\DefMacro{test-results-bl-model0-lc9-num-fail}{1793}
\DefMacro{test-results-bl-model1-lc0-num-fail}{2692}
\DefMacro{test-results-bl-model1-lc1-num-fail}{218}
\DefMacro{test-results-bl-model1-lc2-num-fail}{2304}
\DefMacro{test-results-bl-model1-lc3-num-fail}{416}
\DefMacro{test-results-bl-model1-lc4-num-fail}{445}
\DefMacro{test-results-bl-model1-lc5-num-fail}{829}
\DefMacro{test-results-bl-model1-lc6-num-fail}{1391}
\DefMacro{test-results-bl-model1-lc7-num-fail}{139}
\DefMacro{test-results-bl-model1-lc8-num-fail}{4576}
\DefMacro{test-results-bl-model1-lc9-num-fail}{1262}
\DefMacro{test-results-bl-model2-lc0-num-fail}{3535}
\DefMacro{test-results-bl-model2-lc1-num-fail}{734}
\DefMacro{test-results-bl-model2-lc2-num-fail}{2450}
\DefMacro{test-results-bl-model2-lc3-num-fail}{865}
\DefMacro{test-results-bl-model2-lc4-num-fail}{2124}
\DefMacro{test-results-bl-model2-lc5-num-fail}{2532}
\DefMacro{test-results-bl-model2-lc6-num-fail}{1661}
\DefMacro{test-results-bl-model2-lc7-num-fail}{125}
\DefMacro{test-results-bl-model2-lc8-num-fail}{6440}
\DefMacro{test-results-bl-model2-lc9-num-fail}{1557}

@@

\DefMacro{test-results-model0-lc0-num-seed-fail}{22}
\DefMacro{test-results-model0-lc0-num-exp-fail}{1163}

@@

\DefMacro{test-results-model0-lc1-num-seed-fail}{46}
\DefMacro{test-results-model0-lc1-num-exp-fail}{1680}

@@

\DefMacro{test-results-model0-lc2-num-seed-fail}{24}
\DefMacro{test-results-model0-lc2-num-exp-fail}{932}

@@

\DefMacro{test-results-model0-lc3-num-seed-fail}{42}
\DefMacro{test-results-model0-lc3-num-exp-fail}{1438}

@@

\DefMacro{test-results-model0-lc4-num-seed-fail}{50}
\DefMacro{test-results-model0-lc4-num-exp-fail}{1486}

@@

\DefMacro{test-results-model0-lc8-num-seed-fail}{71}
\DefMacro{test-results-model0-lc8-num-exp-fail}{1723}

@@

\DefMacro{test-results-model0-lc5-num-seed-fail}{12}

@@

\DefMacro{test-results-model0-lc6-num-seed-fail}{15}
\DefMacro{test-results-model0-lc6-num-exp-fail}{182}

@@

\DefMacro{test-results-model0-lc7-num-seed-fail}{2}
\DefMacro{test-results-model0-lc7-num-exp-fail}{17}

@@

\DefMacro{test-results-model0-lc9-num-seed-fail}{2}
\DefMacro{test-results-model0-lc9-num-exp-fail}{37}

@@

\DefMacro{test-results-model1-lc0-num-seed-fail}{13}
\DefMacro{test-results-model1-lc0-num-exp-fail}{725}

@@

\DefMacro{test-results-model1-lc1-num-seed-fail}{41}
\DefMacro{test-results-model1-lc1-num-exp-fail}{1537}

@@

\DefMacro{test-results-model1-lc2-num-seed-fail}{24}
\DefMacro{test-results-model1-lc2-num-exp-fail}{939}

@@

\DefMacro{test-results-model1-lc3-num-seed-fail}{21}
\DefMacro{test-results-model1-lc3-num-exp-fail}{664}

@@

\DefMacro{test-results-model1-lc4-num-seed-fail}{50}
\DefMacro{test-results-model1-lc4-num-exp-fail}{1486}

@@

\DefMacro{test-results-model1-lc8-num-seed-fail}{79}
\DefMacro{test-results-model1-lc8-num-exp-fail}{1947}

@@

\DefMacro{test-results-model1-lc5-num-seed-fail}{28}

@@

\DefMacro{test-results-model1-lc6-num-seed-fail}{17}
\DefMacro{test-results-model1-lc6-num-exp-fail}{160}

@@

\DefMacro{test-results-model1-lc7-num-seed-fail}{2}
\DefMacro{test-results-model1-lc7-num-exp-fail}{19}

@@

\DefMacro{test-results-model1-lc9-num-seed-fail}{1}
\DefMacro{test-results-model1-lc9-num-exp-fail}{57}

@@

\DefMacro{test-results-model2-lc0-num-seed-fail}{20}
\DefMacro{test-results-model2-lc0-num-exp-fail}{1040}

@@

\DefMacro{test-results-model2-lc1-num-seed-fail}{44}
\DefMacro{test-results-model2-lc1-num-exp-fail}{1579}

@@

\DefMacro{test-results-model2-lc2-num-seed-fail}{24}
\DefMacro{test-results-model2-lc2-num-exp-fail}{961}

@@

\DefMacro{test-results-model2-lc3-num-seed-fail}{38}
\DefMacro{test-results-model2-lc3-num-exp-fail}{1280}

@@

\DefMacro{test-results-model2-lc4-num-seed-fail}{50}
\DefMacro{test-results-model2-lc4-num-exp-fail}{1486}

@@

\DefMacro{test-results-model2-lc8-num-seed-fail}{93}
\DefMacro{test-results-model2-lc8-num-exp-fail}{2216}

@@

\DefMacro{test-results-model2-lc5-num-seed-fail}{39}

@@

\DefMacro{test-results-model2-lc6-num-seed-fail}{19}
\DefMacro{test-results-model2-lc6-num-exp-fail}{198}

@@

\DefMacro{test-results-model2-lc7-num-seed-fail}{1}
\DefMacro{test-results-model2-lc7-num-exp-fail}{11}

@@

\DefMacro{test-results-model2-lc9-num-seed-fail}{3}
\DefMacro{test-results-model2-lc9-num-exp-fail}{76}

>>>>

\DefMacro{test-results-bl-model0-lc0-num-fail}{43.87}

@@

\DefMacro{test-results-bl-model0-lc1-num-fail}{11.77}

@@

\DefMacro{test-results-bl-model0-lc2-num-fail}{97.24}

@@

\DefMacro{test-results-bl-model0-lc3-num-fail}{86.00}

@@

\DefMacro{test-results-bl-model0-lc4-num-fail}{88.09}

@@

\DefMacro{test-results-bl-model0-lc5-num-fail}{21.00}

@@

\DefMacro{test-results-bl-model0-lc6-num-fail}{77.51}

@@

\DefMacro{test-results-bl-model0-lc7-num-fail}{0.30}

@@

\DefMacro{test-results-bl-model0-lc8-num-fail}{53.06}

@@

\DefMacro{test-results-bl-model0-lc9-num-fail}{19.48}
\DefMacro{test-results-bl-model1-lc0-num-fail}{31.57}
\DefMacro{test-results-bl-model1-lc1-num-fail}{3.21}
\DefMacro{test-results-bl-model1-lc2-num-fail}{92.31}
\DefMacro{test-results-bl-model1-lc3-num-fail}{41.60}
\DefMacro{test-results-bl-model1-lc4-num-fail}{20.95}
\DefMacro{test-results-bl-model1-lc5-num-fail}{10.36}
\DefMacro{test-results-bl-model1-lc6-num-fail}{81.06}
\DefMacro{test-results-bl-model1-lc7-num-fail}{1.61}
\DefMacro{test-results-bl-model1-lc8-num-fail}{59.86}
\DefMacro{test-results-bl-model1-lc9-num-fail}{13.71}
\DefMacro{test-results-bl-model2-lc0-num-fail}{41.45}
\DefMacro{test-results-bl-model2-lc1-num-fail}{10.82}
\DefMacro{test-results-bl-model2-lc2-num-fail}{98.16}
\DefMacro{test-results-bl-model2-lc3-num-fail}{86.50}
\DefMacro{test-results-bl-model2-lc4-num-fail}{100.00}
\DefMacro{test-results-bl-model2-lc5-num-fail}{31.65}
\DefMacro{test-results-bl-model2-lc6-num-fail}{96.79}
\DefMacro{test-results-bl-model2-lc7-num-fail}{1.44}
\DefMacro{test-results-bl-model2-lc8-num-fail}{84.25}
\DefMacro{test-results-bl-model2-lc9-num-fail}{16.92}

@@

\DefMacro{test-results-model0-lc0-num-seed-fail}{44.00}
\DefMacro{test-results-model0-lc0-num-exp-fail}{50.06}

@@

\DefMacro{test-results-model0-lc1-num-seed-fail}{92.00}
\DefMacro{test-results-model0-lc1-num-exp-fail}{94.17}

@@

\DefMacro{test-results-model0-lc2-num-seed-fail}{92.31}
\DefMacro{test-results-model0-lc2-num-exp-fail}{92.37}

@@

\DefMacro{test-results-model0-lc3-num-seed-fail}{84.00}
\DefMacro{test-results-model0-lc3-num-exp-fail}{88.00}

@@

\DefMacro{test-results-model0-lc4-num-seed-fail}{100.00}
\DefMacro{test-results-model0-lc4-num-exp-fail}{100.00}

@@

\DefMacro{test-results-model0-lc8-num-seed-fail}{71.00}
\DefMacro{test-results-model0-lc8-num-exp-fail}{72.43}

@@

\DefMacro{test-results-model0-lc5-num-seed-fail}{24.00}

@@

\DefMacro{test-results-model0-lc6-num-seed-fail}{78.95}
\DefMacro{test-results-model0-lc6-num-exp-fail}{86.67}

@@

\DefMacro{test-results-model0-lc7-num-seed-fail}{4.00}
\DefMacro{test-results-model0-lc7-num-exp-fail}{4.31}

@@

\DefMacro{test-results-model0-lc9-num-seed-fail}{4.00}
\DefMacro{test-results-model0-lc9-num-exp-fail}{2.69}

@@

\DefMacro{test-results-model1-lc0-num-seed-fail}{26.00}
\DefMacro{test-results-model1-lc0-num-exp-fail}{31.21}

@@

\DefMacro{test-results-model1-lc1-num-seed-fail}{82.00}
\DefMacro{test-results-model1-lc1-num-exp-fail}{86.15}

@@

\DefMacro{test-results-model1-lc2-num-seed-fail}{92.31}
\DefMacro{test-results-model1-lc2-num-exp-fail}{93.06}

@@

\DefMacro{test-results-model1-lc3-num-seed-fail}{42.00}
\DefMacro{test-results-model1-lc3-num-exp-fail}{40.64}

@@

\DefMacro{test-results-model1-lc4-num-seed-fail}{100.00}
\DefMacro{test-results-model1-lc4-num-exp-fail}{100.00}

@@

\DefMacro{test-results-model1-lc8-num-seed-fail}{79.00}
\DefMacro{test-results-model1-lc8-num-exp-fail}{81.84}

@@

\DefMacro{test-results-model1-lc5-num-seed-fail}{56.00}

@@

\DefMacro{test-results-model1-lc6-num-seed-fail}{89.47}
\DefMacro{test-results-model1-lc6-num-exp-fail}{76.19}

@@

\DefMacro{test-results-model1-lc7-num-seed-fail}{4.00}
\DefMacro{test-results-model1-lc7-num-exp-fail}{4.82}

@@

\DefMacro{test-results-model1-lc9-num-seed-fail}{2.00}
\DefMacro{test-results-model1-lc9-num-exp-fail}{4.15}

@@

\DefMacro{test-results-model2-lc0-num-seed-fail}{40.00}
\DefMacro{test-results-model2-lc0-num-exp-fail}{44.77}

@@

\DefMacro{test-results-model2-lc1-num-seed-fail}{88.00}
\DefMacro{test-results-model2-lc1-num-exp-fail}{88.51}

@@

\DefMacro{test-results-model2-lc2-num-seed-fail}{92.31}
\DefMacro{test-results-model2-lc2-num-exp-fail}{95.24}

@@

\DefMacro{test-results-model2-lc3-num-seed-fail}{76.00}
\DefMacro{test-results-model2-lc3-num-exp-fail}{78.34}

@@

\DefMacro{test-results-model2-lc4-num-seed-fail}{100.00}
\DefMacro{test-results-model2-lc4-num-exp-fail}{100.00}

@@

\DefMacro{test-results-model2-lc8-num-seed-fail}{93.00}
\DefMacro{test-results-model2-lc8-num-exp-fail}{93.15}

@@

\DefMacro{test-results-model2-lc5-num-seed-fail}{78.00}

@@

\DefMacro{test-results-model2-lc6-num-seed-fail}{100.00}
\DefMacro{test-results-model2-lc6-num-exp-fail}{94.29}

@@

\DefMacro{test-results-model2-lc7-num-seed-fail}{2.00}
\DefMacro{test-results-model2-lc7-num-exp-fail}{2.79}

@@

\DefMacro{test-results-model2-lc9-num-seed-fail}{6.00}
\DefMacro{test-results-model2-lc9-num-exp-fail}{5.54}

### 2022-05-06 paper/ase22/tables/test-results-table.tex
exp restuls

\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.4cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.3cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\

>>>>

\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\
